A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.

### 2022-03-30 tex/response.tex

\documentclass[utf8]{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\usepackage{natbib}

% import Eq and Section references from the main manuscript where needed
\usepackage{xr}
\externaldocument{manuscript}
% \externaldocument{methods}
\externaldocument{supplementary}

\newcommand{\linerange}[2]{%
\ifthenelse{\equal{\getrefnumber{#1}}{\getrefnumber{#2}}}{%
line \ref{#1}%
}{%
lines \ref{#1}--\ref{#2}%
}%
}
% package needed for optional arguments
\usepackage{xifthen}
\renewcommand{\thefigure}{R\arabic{figure}}

\usepackage{url,hyperref,lineno,microtype}

\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{xr}
\usepackage{bm}
\usepackage{cases}

\graphicspath{{../figures/}}

\setcounter{section}{0}
\newcounter{point}[section]
\setcounter{point}{0}

% command declarations for reviewer points and our responses

\newenvironment{point}
{\refstepcounter{point} \bigskip \noindent {\textbf{Point~P\thesubsection.\arabic{point}} } ---\ }
{\par }

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent
	{\textbf{Point~P\thesubsection.\arabic{point}} } ---~#1\par }

\newenvironment{reply}
{\medskip \noindent Reply:\  }
		{\medskip}

\newcommand{\shortreply}[2][]{\medskip \noindent Reply:\  #2
		\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
		\medskip}

\begin{document}
% \onecolumn
% \firstpage{1}

\begin{center}
	\Large Response to the reviewers
\end{center}
We thank the reviewers for their critical assessment of our work.
The biggest changes in the revised manuscript came as a result of points \hyperref[p:biol]{P2.1.1} and \hyperref[p:gstar]{P2.3.8}, which led us to revert our model to the original equations and parameter values used in \cite{bose2011}.
The motivation behind a slightly different model in our original manuscript, as well as the consequence of the latest changes in the revised manuscript are given in \cref{sec:model}.
Both reviewers also pointed out that some of our notation and terminology is unclear.
As a result we renamed many of the terms, an overview of the most important terms is given in \cref{sec:terminology}.

We will refer to the first version of the manuscript that was submitted to the journal as ``original manuscript'' (M0), and we will call the latest submitted version the ``revised manuscript'' (M1).
If not otherwise stated, the equations numbers, figures, and line numbers refer to the revised manuscript.
This response is structured as follows:
\Cref{sec:sum} contains the terminology as well as summarises the main model changes in the revised manuscript.
In \cref{sec:r1} we address the concerns raised by reviewer 1, and in \cref{sec:r1} the concerns raised by reviewer 2.

\section{Summary of changes}
\label{sec:sum}

\subsection{Terminology and notation}
\label{sec:terminology}
To increase clarity we have changed some of the terminology.
Below we briefly define the controversial terms.
In the context of a spiking limit cycle of an uncoupled Morris-Lecar (ML) cell we have:
\begin{itemize}
	\item $T_{a}$: The time interval when the voltage is above firing threshold, i.e. when $v>v_{\theta}$.
	\item $T_{s}$: The time interval when the voltage is below firing threshold, i.e. when $v<v_{\theta}$.
\end{itemize}
In the context of a stable $n:n$ solution we have:
\begin{itemize}
	\item \textbf{Active cell}: Cell that is currently firing.
	\item \textbf{Silent cell}: Cell that is currently suppressed and does not fire.
	\item \textbf{Active phase}: Time interval between the start of the limit cycle and the time when the voltage of the active cell falls below firing threshold after the $n$th spike, i.e. for $t \in \left[0, (n-1)T + T_{a}\right]$.
	\item \textbf{Silent phase}: Time interval after the end of the active phase and the cycle period, i.e. for $t \in \left[(n-1)T + T_{a}, P\right]$.
	\item \textbf{Active phase map}: Map $F_{n}$ that models the evolution of $d$ during the active phase.
	\item \textbf{Recovery phase map}: Map $Q_{n}$ that models the evolution of $d$ during the silent phase.
	\item \textbf{Left and right branch borders}: The left and right branch borders of stable $n:n$ solutions are denoted by $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$, respectively.
\end{itemize}

\subsection{Model changes}
\label{sec:model}
% Overview
In this section we first explain the model differences between the \cite{bose2011} paper and our original manuscript.
We will then outline a short motivation for these changes.
Finally the model of the revised manuscript is discussed.
There are two main differences in the model equations and parameters between the original manuscript and \cite{bose2011}:
First, the value of the applied current $I$ is different: In \cite{bose2011} they have $I=3.8$ $\si{\mu A/cm^2}$, in the original manuscript we had $I=3.8$ $\si{\mu A/cm^2}$.
Second, the original manuscript used step-wise resets of $d$ and $s$ to simplify the dynamics of the active state of the spike (when $v > v_{\theta}$).

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\textwidth]{model-changes}
	\caption{Nullclines of the \cite{bose2011} ML model with $I=3.8$ $\si{\mu A/cm^2}$ (left), and the model from our original manuscript with $I=6$ $\si{\mu A/cm^2}$ (right). The solid blue lines are the $v$-nullclines when $\bar g s=0$. The dashed blue lines are the $v$-nullclines when $\bar g s$ is near the respective bifurcation point where the fixed point changes stability.\label{fig:nullclines}}
\end{figure}

The main motivation for increasing $I$ in the original manuscript had to do with the excitability of a silent ML cell, and was to simplify the explanation of the concept of the ``release conductance''.
\Cref{fig:nullclines} shows the $v$- and $w$-nullclines for $I=3.8$ $\si{\mu A/cm^2}$ (left) and for $I=6$ $\si{\mu A/cm^2}$ (right) when no inhibition is applied and $g = 0$ (let $g:= \bar g s$).
The dashed lines indicate the $v$-nullcline at the bifurcation point when the total synaptic conductance $g$ is at the respective bifurcation value, $g=g_{bif}$.
In case of $I=3.8$ $\si{\mu A/cm^2}$ we have $g_{bif}\approx 0.007$ $\si{\mu A/cm^2}$, whereas for $I=6$ $\si{\mu A/cm^2}$ we have $g_{bif}\approx 0.03804$ $\si{\mu A/cm^2}$.
Hence for $I=3.8$ $\si{\mu A/cm^2}$ and $g=0$, the unstable fixed point is ``closer'' in phase space to the stable fixed point at bifurcation when $g=g_{bif}$, than in case of $I=6$ $\si{\mu A/cm^2}$.
In other words, a silent cell with $I=3.8$ $\si{\mu A/cm^2}$ is ``easier to excite'' than a silent cell with $I=6$ $\si{\mu A/cm^2}$.

In contrast to the $I=6$ $\si{\mu A/cm^2}$ scenario, when $I=3.8$ $\si{\mu A/cm^2}$ the bifurcation at $g=g_{bif}$ is not sufficient to accurately predict the release time of the silent cell, as the silent cell can produce a first spike despite $g > g_{bif}$.
Why this happens is interesting but not trivial, and we believe that at this stage it is not important.
However, when $I=6$ $\si{\mu A/cm^2}$ the condition $g>g_{bif}$ becomes sufficient to accurately predict the release time of the silent cell, that is assuming $n>1$ and with the exception of the $2:2$ outliers in fig. 6 (original manuscript).
When $g>g_{bif}$ is sufficient for predicting the release time, the definition of the release conductance $g^\star$ becomes straightforward, that is $g^\star=g_{bif}$.
Moreoever, the value of $g^\star$ can be computed numerically, for example using AUTO.
The downside of using $I=6$ $\si{\mu A/cm^2}$ is that finding $g^\star$ analytically becomes difficult.
Because reviewer 1 asked for an analytic derivation of $g^\star$ in point \hyperref[p:gstar]{P2.3.8}, and to avoid more confusion by using a different model than \cite{bose2011}, we decided to use $I=3.8$ $\si{\mu A/cm^2}$ in the revised manuscript.
As explained above, however, this comlicates the definition and explanation of $g^\star$:
Now the actual value of the release conductance (as defined by the value of $g$ at the first spike time of the silent cell) depends on both $n$ and $\bar g$, as we illustrate in \cref{fig:gstar-diag}A.
But as the graph also shows, the dashed line appears to be a good approximation for the numerically computed release conductances.
This line marks the value of $g$ of a suppressed and $\bar g= \bar g_s$, at the end of a cycle.
Here that $\bar g_s$ is smallest value of $\bar g$ that produces the suppressed solution.
And this values is easy to express analytically:
\begin{equation}
	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
\end{equation}
Another advantage of using $I=3.8$ $\si{\mu A/cm^2}$ is that all release delays are on the millisecond scale, and there are no more outliers such the branch B in fig. 6 (M0).

The main motivation for changing the synapse model was mathematical convenience, as it made the $\Pi_{n}$-map formulation more readable.
This change does not appear to affect the overall picture, i.e. the period bifurcation diagram has a similar shape even after our change, e.g. compare fig. 4A (M0) to \cref{fig:bif-diagram} (M1).
However, the biological realism of the step-wise resets of $s$ and $d$ in the original manuscript were correctly questioned by reviewer 1 in \hyperref[p:biol]{P2.1.1}.
We hope that reverting to the original equations used in \cite{bose2011} solves this concern.

To sum up the model changes:
The revised manuscript has $I=3.8$ $\si{\mu A/cm^2}$, and synaptic dynamics are modelled by

\begin{align*}
	\dot d & =
	\begin{cases}
		(1-d)/\tau_{a} & \text{ if }\, v<v_{\theta}, \\
		-d/\tau_{b}    & \text{ if }\, v>v_{\theta},
	\end{cases}
\end{align*}

\begin{align*}
	\dot s & =
	\begin{cases}
		-s/\tau_{\kappa} & \text{ if }\, v<v_{\theta}, \\
		0                & \text{ if }\, v>v_{\theta},
	\end{cases}
\end{align*}
and we set $s=d$ while $v>v_{\theta}$.
All equations and derivation in the process of the construction of $\Pi_n$ were modified accordingly.
It is important not note that $\lambda$ is a \textit{derived} parameter in the revised manuscript:
\begin{equation}
\lambda := \exp(-T_s/\tau_a).
\end{equation}
Naturally all the data for all figures was recomputed with the new model.
Fig. 5 (M0) was removed.
Because $g^\star$ is not defined by the Hopf-bifurcation in the revised manuscript, an illustration of the nullclines as $\bar g s$ is varied seems to be of minor importance.
Fig. 6 (M0) was also removed, since the new definition of $g^\star$ does not produce a significant release delay.

\subsection{Other minor changes}

\begin{itemize}
	\item In Fig. 1 (M0) we removed the four phases of a spike (``active'', ``silent'', ``jump up'', ``jump down''). We did this to reduce the terminology confusion regarding ``free''/``quite'' vs ``active''/``silent'', pointed out by reviewer 1 in P2.2.1. As suggested by the reviewer, in the revised manuscript we use ``active''/``silent'' to refer to the two phases of burst only.
	\item Fig. 4B (M0) was removed, as $IBI$ is not clearly defined and is confusing.
	\item $T_{act}$ and $T_{inact}$ were renamed to $T_a$ and $T_s$, respectively.
	\item $\bar g_{+}$ and $\bar g_{-}$ were renamed to $\bar g_{\mathcal{L}}$ and $\bar g_{\mathcal{R}}$, as a response to point P2.3.19 raised by reviewer 1.
\end{itemize}

\section{Reviewer 1}
\label{sec:r1}
\subsection{Major Comments}
\setcounter{point}{0}

\begin{point}
\label{p:biol}
I don't see the justification for assuming $\dot d=(1-d)/\tau_{d}$ when a neuron is ACTIVE (see below for ``active'' meaning).
Can the authors provide some biological justification that the available synaptic resources actually increase during a spike?
If not, it seems critical that they give some other justification that this assumption is OK.
\end{point}
\begin{reply}
We agree with the reviewer's criticism.
Beyond mathematical convenience there was no biological justification for making the assumption that the depression variable recovers when $v>v_{\theta}$.
In the original model from \cite{bose2011} $d$ decays when $v>v_{\theta}$:
\begin{align*}
  \dot d_{i} &= \begin{cases}
  (1-d_{i})/\tau_{a} &  \text{ if } v_{i}<v_{\theta},
  \\
  -d_{i}/\tau_{b}    &  \text{ if } v_{i}>v_{\theta},
  \end{cases}
\end{align*}
which is now also used in the revised manuscript, see eq. (\ref{eq:dot-d-up}) and (\ref{eq:dot-d-down}).
\end{reply}

\shortpoint{The authors assume that each spike has duration $T$. But that can only be true exactly if the $s$ variable from the silent neuron is 0, which is never the case. The authors should compute how fast $s$ has to decay to make period=T a reasonable approximation even in the first spike of a burst, and some commentary about this should be given.}
\begin{reply}
We agree that $\tau_{\kappa}$ is important for the $ISI=T$ assumption.
The paragraph outlining the is assumption in \cref{sec:assumptions} of the main text has been edited to highlight the importance of $\tau_{\kappa}$ for the validity of that assumption.
We have also added \cref{sec:tauk} to the Supplementary Material where we numerically explore how changing the value of $\tau_{\kappa}$ affects the first, second, and third $ISI$. There we come to the conclusion that for $\tau_{\kappa} \leq 100$ $\si{ms}$ the effect of a non-zero $s$ at the start of the active phase is negligible for the first, and naturally the subsequent, $ISI$s.
\end{reply}

\subsection{Terminology}
\setcounter{point}{0}

\begin{point}
	First, the authors refer to the neurons as ``free'' or ``quiet'' and refer to the ``free phase'' and ``quiet phase''.
	They say that they follow Bose and Booth in doing so.
	But I have read (and written) MANY papers on bursting\slash CPGs\slash multi-phase solutions, and they always refer to ``active'' and ``silent'' rather than ``free'' and ``quiet''.
	The authors should switch their word use as well to avoid confusing the field.
\end{point}
\begin{reply}
	We agree that the ``free''\slash``quiet'' terminology is uncommon in the field.
	When referring to a cell in the context of $n:n$ limit cycles, apart from being consistent with \citet{bose2011}, our original intent was to use the ``free''\slash``quiet'' terms to distinguish them from the phases of the action potential, where we used the more common ``active''\slash ``silent'' terms.
	However, as reviewer 1 has pointed out, using ``active''\slash``silent'' to refer to both the phases of a spiking limit cycle \cite[e.g.~p.~250]{ermentrout2010}, and the bursting limit cycle \cite[e.g.~p.~103]{ermentrout2010} (at least in the context of ``bursty'' single cells) appears to be more common in the field.
	For the construction of $\Pi_{n}$ only the distinction between the active ($v>v_{\theta}$) and quiet ($v<v_{\theta}$) states of an action potential, and the associated times intervals $T_{a}$ and $T_{s}$, are essential.
	To reduce confusion we have therefore removed the mention of the ``four phases of a spike'' (lines 112-118 in M0), such that in the new version of the manuscript ``active'' and ``silent'' refer exclusively to the phases of a $n:n$ solution.
	We hope that this clarification is sufficient to be consistent with the field, but if this is still confusing we are open for further naming suggestions.
\end{reply}

\shortpoint{Second, the authors use $ISI$ and $IBI$ incorrectly. The $ISI$ is the inter-spike interval. This is the period BETWEEN spikes, NOT the entire period T of a spiking event (see e.g., line 181). The $IBI$ is the inter-burst interval. In this paper, that would be the silent phase duration for one neuron. It is NOT the entire period of a bursting event, nor is it the delay from the end of one neuron’s active phase to the start of the other neuron’s active phase (e.g., line 266). These need to be corrected throughout the paper.}
\begin{reply}
We agree with the reviewer that the $IBI$ notation is misleading, and it has been completely removed from the manuscript.
For the inter-spike-interval $ISI$ we have used what we believe is the standard definition \cite[e.g. see][]{ermentrout1998,bose2011,matveev2007}:
The $ISI$ is the time interval between successive spike times, where a spike time is the time when the voltage crosses the firing threshold upwards, i.e. the time when $v$ changes from being below the firing threshold to being above it. In the case of an uncoupled ML cell we have $ISI=T$.
If this definition of the $ISI$ is not common in the field, then we kindly ask the reviewer to point us to references where a different, more common definition is used.
\end{reply}

\shortpoint{Third, in the Results, the authors state the signs of various derivatives without proof. Some are obvious (e.g., eqn. (30)) but others, such as eqn. (31), are not. Some brief justification is needed.}
\begin{reply}
Agreed. We have added a brief explanation regarding the monotonicity of $\Pi_{n}$ w.r.t. $d^{\star}$ (line \ref{line:mono}), which follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
Showing $\dv*{Q_{n}}{\Delta t} > 0$ and $\dv*{F_{n}}{d^{\star}} > 0$ for our model parameters is uncomplicated.
\end{reply}

\shortpoint{Fourth, Fig. 11A seems to contrast with Fig. 4A. Fig. 11A seems to show massive multistability of solutions for different $n$, whereas Fig. 4A only has bistability. Some clarification is needed}
\shortreply{Figure 11A (M0) shows stable fixed points of $\Pi_{n}$ for different $n$. Figure 4A (M0) shows the period of stable $n:n$ solutions for the flow system. The map $\Pi_{n}$ relies on the assumption that the active phase contains exactly $n$ spikes. This assumption is only valid on certain intervals of $\bar g$, namely those defined by $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$. We have added some additional clarification in line \ref{line:ll}.}

### 2022-03-30 tex/manuscript.tex
Update a bunch of tex files

\documentclass[utf8, draft]{frontiersFPHY} % for Physics and Applied Maths
% \documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{physics}
\usepackage{cases}
\usepackage{bm}
% This should make nicer typesetting and lead to feaver underfull/overfull box errors
\usepackage{microtype}

@@

\graphicspath{{../figures/}}

@@

% Define terms for "free"/"quiet"
\newcommand{\free}{free}
\newcommand{\suppressed}{suppressed}

@@

\begin{abstract}
  \section{}
  Short-term synaptic plasticity is found in many areas of the central nervous system.
  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
  We derive conditions that describe period-increment bifurcations between stable $n:n$ and $(n+1):(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.

  \tiny
  \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}

\end{abstract}

@@

\section*{Data Availability Statement}
The datasets generated for this study are available on request to the corresponding author.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-uncoupled.pdf}
  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$
    Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue,
    $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$
    is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace
    $v(t)$ of an action potential.~\label{fig:nullclines}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/depression-traces.pdf}
  \caption{Solution profiles of a $4-4$ burst. $\bm{\mathrm{(A)}}$ Membrane potentials
    of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange). $\bm{\mathrm{(B)}}$
    Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell
    1.~\label{fig:depression-traces}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/burst-sols.pdf}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing
    values of the coupling strength $\gbar$ (increasing top to
    bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable $n:n$ solutions for
    increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
    solutions. Dashed lines show the interval between the $5-5$ and the suppressed
    solutions, where higher period $n:n$ solutions occur on increasingly smaller intervals
    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n:n$ solutions in
    $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
    $ISI$s with the free phase. During the free phase, $ISI$s are of approximately
    constant duration $T$.\label{fig:bif-diagram}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-coupled.pdf}
  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
  $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
  s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
  point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
  $p_{f}$ changes stability (half orange,  half blue point) at some critical total
  conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
  $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of
    the three branches (A, B, C) also shows the timecourse of the total synaptic
    conductance $\gbar s$ of a sample stable solution of both cells (blue and orange),
    as well as the release conductance $g^{\star}$ (dashed green line).
    $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet
    cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with
    a long release delay associated with a subset of $2-2$ solutions. Here the release
    condition is briefly satisfied after the first spike of cell 1. This does not cause
    firing of cell 2, which only occurs after the second spike of cell 1.
    $\bm{\mathrm{(C)}}$ Branch with $n:n$ solutions  where release delay is
    approximately zero and the release condition is sufficient for firing of cell 2.
    ~\label{fig:release-delay}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/free-quiet.pdf}
  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
    $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
    The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total
    synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance
    $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell
    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/FQ-map.pdf}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
  $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
  $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/Pn-map.pdf}
  \caption{Map $\Pi_{n}:d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
  at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
  varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is
  illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/folds.pdf}
  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves)
    and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
    $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the
    corresponding solution period from numerical integration of the system of ODEs
    (orange).~\label{fig:folds}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
    \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of
    the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

>>>>

\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{physics}
\usepackage{cases}
\usepackage{bm}
% This should make nicer typesetting and lead to feaver underfull/overfull box errors
\usepackage{microtype}

@@

\graphicspath{{../figures}}

@@

\usepackage{xr}
\externaldocument{supplementary}

% Define terms for "free"/"quiet"
\newcommand{\free}{active}
\newcommand{\suppressed}{silent}

@@

@@

\section*{Data Availability Statement}
The data sets generated for this study are available on request to the corresponding author.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{nullclines}
  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$
    Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue,
    $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$
    is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace
    $v(t)$ of an action potential.~\label{fig:nullclines}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{burst-sols}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing
    values of the coupling strength $\gbar$ (increasing top to
    bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{bif-diagram}
  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\gbar$. Dashed lines show the interval between the $5-5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\gbar$.\label{fig:bif-diagram}}
\end{figure}

% \begin{figure}[h!]
%   \centering
%   \includegraphics{nullclines-coupled}
%   \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
%   $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
%   s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
%   point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
%   $p_{f}$ changes stability (half orange,  half blue point) at some critical total
%   conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
%   $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
% \end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{gstar-diag}
  \caption{Numerically computed values of the release conductance ($\tilde g^{\star}$) for various $n:n$ solutions. The dashed line indicates the analytical approximation of the release conductance by $g^{\star}$.\label{fig:gstar-diag}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{free-quiet}
  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
    $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
    The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total
    synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance
    $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell
    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{delta-t}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
    T$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{FQ-maps}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
  $\gbar=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
  $d^{\star}=d_{s}$ which is indicated by a dashed vertical line. Curves $Q_n$ intersect at $\Delta t = \tau_{\kappa}\ln\Big(\bar g / g^{\star}\Big)$. \label{fig:FQ-maps}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{Pn-map}
  \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
  at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
  varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is
  illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{folds}
  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves)
    and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
    $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points of $\Pi_{n}$ (blue), and the corresponding periods from stable $n:n$ solutions acquired via numerical integration of the system of ODEs
    (orange).~\label{fig:folds}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{final-bif}
  \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
    \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
\end{figure}
